Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-05-10 Cover_letter_JPM.tex
Updates from Overleaf

\subsection*{1-1}
\begin{MyColorPar}{blue}
First of all, please describe the difference between the two manuscripts.
\end{MyColorPar}
%The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.

@@

Answer

@@

2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).

%[我的 candidate 中為什麼沒有 EGFR];  
%In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
%by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
%(please see https://github.com/texchi2/\linebreak
%pvalueTex/blob/master/HNSCC\_OS\_marginS\_6429.csv for reference, the table was ranked by FDR P-value)

@@

\subsection*{1-2}
\begin{MyColorPar}{blue}
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.
\end{MyColorPar}
%DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]

%\begin{MyColorPar}{blue}
Answer

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129). Also, it was shown here in the following paragraph.
\begin{MyColorPar}{red}
"
"
\end{MyColorPar}

%Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation), 
%epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
%The usefulness of multi-omics data for the prediction of HNSCC outcome %is expected.
%such as the (censored) survival time.

\end{MyColorPar}
\pagebreak
%======
\section*{Response to Reviewer 2 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

@@

\subsection*{2-1}
\begin{MyColorPar}{blue}
Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
\end{MyColorPar}

%
Answer

@@

%***=> Bonferroni correction should be used in final decision.

@@

\subsection*{2-2}
\begin{MyColorPar}{blue}
I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone
\end{MyColorPar}

%
Answer

@@

\subsection*{2-3}
\begin{MyColorPar}{blue}
% strategy should changing
In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01. Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. The p-values are affected by the sample size, which should be described in the main text. As I mentioned above, the authors should look for more data to verify these biomarkers.
\end{MyColorPar}

%
Answer

@@

% #####################
\subsection*{2-4}
\begin{MyColorPar}{blue}
How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
\end{MyColorPar}

%
Answer

@@

@@

\subsection*{2-5}
\begin{MyColorPar}{blue}
Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
\end{MyColorPar}
%
Answer

@@

\subsection*{2-6}
\begin{MyColorPar}{blue}
[Minor comments]
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.
\end{MyColorPar}

%
Answer

@@

%%
\begin{MyColorPar}{blue} % minor comment
***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
\end{MyColorPar}

@@

%%%***[latex line 410]
\begin{MyColorPar}{blue} % minor comment
In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.
\end{MyColorPar}

@@

% the end of response rebuttal %%%%%%%%%%%%

@@

>>>>

\subsection*{1-1}
%\begin{MyColorPar}{blue}
First of all, please describe the difference between the two manuscripts.

%The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.

@@

@@

2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).
\end{MyColorPar}

%% x
%[我的 candidate 中為什麼沒有 EGFR];  
%In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
%by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
%(please see https://github.com/texchi2/\linebreak
%pvalueTex/blob/master/HNSCC\_OS\_marginS\_6429.csv for reference, the table was ranked by FDR P-value)

@@

\subsection*{1-2}
%
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.

%DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129). Also, it was shown here in the following paragraph.
\begin{MyColorPar}{red}
"
"
\end{MyColorPar} %red
\end{MyColorPar} % blue
%Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation), 
%epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
%The usefulness of multi-omics data for the prediction of HNSCC outcome %is expected.
%such as the (censored) survival time.

%======
\section*{Response to Reviewer 2 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

@@

\subsection*{2-1}

Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.

%
\begin{MyColorPar}{blue}
Answer

@@

\end{MyColorPar}
%***=> Bonferroni correction should be used in final decision.

@@

\subsection*{2-2}

I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone

%
\begin{MyColorPar}{blue}
Answer

@@

%
\end{MyColorPar}

\subsection*{2-3}

% strategy should changing
In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01. Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. The p-values are affected by the sample size, which should be described in the main text. As I mentioned above, the authors should look for more data to verify these biomarkers.

%
\begin{MyColorPar}{blue}
Answer

@@

% #####################
\subsection*{2-4}

How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?

%
\begin{MyColorPar}{blue}
Answer

@@

\end{MyColorPar}% end of answer 2.4

@@

\subsection*{2-5}

Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.

%
\begin{MyColorPar}{blue}
Answer

@@

\end{MyColorPar}
%

\subsection*{2-6}
[Minor comments]
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.

%
\begin{MyColorPar}{blue}
Answer

@@

%%
\begin{MyColorPar}{black} % minor comment
***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
\end{MyColorPar}

@@

%%%***[latex line 410]
\begin{MyColorPar}{black} % minor comment
In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.
\end{MyColorPar}

@@

\end{MyColorPar} % end of red

\end{MyColorPar} % end of blue answer 2-6
% the end of response rebuttal %%%%%%%%%%%%

@@

%%%
